---
title: "GMCF Pickleball Utilization, January 2026"
format: 
  dashboard:
    theme: zephyr
    orientation: columns
---

```{r}
library(tidyverse)
library(scales)
library(plotly)
library(reactable)
library(reactablefmtr)
library(tsibble)

options("lubridate.week.start" = 1)

by_session <- read_rds("data/by_session.rds") |> 
  filter(month(date_time) == 1, year(date_time) == 2026)

by_session_trend <- read_rds("data/by_session.rds") |> 
  filter(between(as.Date(date_time), as.Date("2025-10-01"), as.Date("2026-01-31")))

player_dupr_id_name_lookup <- read_rds("data/player_dupr_id_name_lookup.rds")
# player_id_dupr_lookup <- read_rds("data/player_id_dupr_lookup.rds")

session_player_long <- read_rds("data/session_player_long.rds") |> 
  left_join(player_dupr_id_name_lookup, join_by(player_id))|> 
  filter(month(date_time) == 1, year(date_time) == 2026)

theme_set(theme_minimal())

summarize_session <- function(x) {
  x |> 
    summarize(
      n_session_avail = n(),
      n_session_run = sum(session_run),
      run_rate = n_session_run / n_session_avail,
      n_spots_avail = sum(spots),
      n_spots_filled = sum(registered),
      fill_rate = n_spots_filled / n_spots_avail,
      n_spots_avail_run = sum(spots[session_run]),
      n_spots_filled_run = sum(registered[session_run]),
      fill_rate_run = n_spots_filled_run / n_spots_avail_run,
      mean_dupr = weighted.mean(mean_dupr, spots, na.rm = TRUE)
  )
}

session_summary_trend <- by_session_trend |> 
  group_by(ym = yearmonth(date_time)) |> 
  summarize_session()

session_summary_level_trend <- by_session_trend |> 
  group_by(ym = yearmonth(date_time), level) |> 
  summarize_session()

session_summary_level <- by_session |> 
  group_by(level) |> 
  summarize_session()

session_summary <- by_session |> 
  summarize_session()

session_summary_level <- by_session |> 
  group_by(level) |> 
  summarize_session()

player_level_wide <- session_player_long |> 
  filter(!is.na(player_id)) |> 
  count(player_id, level) |> 
  group_by(player_id) |> 
  mutate(total = sum(n)) |> 
  ungroup() |> 
  pivot_wider(names_from = level, values_from = n, values_fill = 0)

by_player <- player_level_wide |> 
  left_join(player_dupr_id_name_lookup, join_by(player_id))

player_rating_range <- 
  session_player_long |>
  filter(!is.na(player_id)) |>
  count(player_id, rating, reliability) |> 
  mutate(dupr_range = case_when(
    rating < 2.8 ~ "< 2.8",
    between(rating, 2.8, 3.3) ~ "2.8–3.3",
    between(rating, 3.3, 3.8) ~  "3.3–3.8",
    between(rating, 3.8, 4.3) ~ "3.8–4.3",
    rating > 4.3 ~ "> 4.3",
    TRUE ~ "No rating"
    ),
    dupr_range = fct_relevel(
      dupr_range, "No rating", "< 2.8", "2.8–3.3", "3.3–3.8", "3.8–4.3", "> 4.3"
    )
    )

rating_player_summary <- player_rating_range |>
  count(dupr_range)

player_summary <- by_player |> 
  summarize(
    n_players = n(),
    mean = mean(total),
    median = median(total),
    max = max(total),
    mean_dupr = mean(rating, na.rm = TRUE),
    median_dupr = median(rating, na.rm = TRUE),
    )

player_summary_by_dupr_range <- by_player |>
  left_join(player_rating_range, join_by(player_id)) |> 
  group_by(dupr_range) |> 
  summarize(
    n_players = n(),
    mean = mean(total),
    median = median(total),
    max = max(total)
    )

level_colors <- c(
  `2.3–3.0` = "#fdd841",
  `2.8–3.5` = "#ff8214",
  `3.3–4.0` = "#1778a3",
  `3.8–4.5` = "#00AAA9",
  `4.3+`    = "#78B728"
)
```

# Court Usage

## Column 1 - value boxes {width=33%}

```{r}
#| content: valuebox
#| title: "Sessions run"
list(
  icon = "calendar-check",
  color = "#D6EFE1",
  value = comma(session_summary$n_session_run)
)
```

```{r}
#| content: valuebox
#| title: "Sessions available"
list(
  icon = "calendar-event",
  color = "#e6f2fd",
  value = comma(session_summary$n_session_avail)
)
```


```{r}
#| content: valuebox
#| title: "Spots filled"
list(
  icon = "person-check-fill",
  color = "#D6EFE1",
  value = comma(session_summary$n_spots_filled)
)
```

```{r}
#| content: valuebox
#| title: "Spots available"
list(
  icon = "ticket",
  color = "#e6f2fd",
  value = comma(session_summary$n_spots_avail)
)
```

## Column 2 = plots

### Run rate {.tabset}

#### Run rate total

```{r}
plot_ly(
  domain = list(x = c(0, 1), y = c(0, 1)),
  value = session_summary$run_rate,
  title = list(text = "Run rate"),
  type = "indicator",
  mode = "gauge+number",
  number = list(valueformat = ".0%"),
  gauge = list(
    bar = list(thickness = 1, color = "steelblue"),
    steps = list(list(range = list(0, 1), color = "#e5e5e5")),
    borderwidth = 0,
    axis = list(range = list(0, 1),tickformat = ".0%")
    )
  ) |> 
  config(displayModeBar = FALSE) |> 
  layout(
    font = list(family = "Inter"),
    margin = list(t = 40, r = 40, b = 10, l = 30)
    )
```

#### By level

```{r}
p <- session_summary_level |> 
  mutate(
    tooltip = paste0(
      "<b>", level, "</b><br>",
      "Run rate: ", percent(run_rate, 1), "<br>",
      "Sessions run: ", n_session_run, "<br>",
      "Sessions available: ", n_session_avail, "<br>"
      )
    ) |> 
  ggplot(aes(run_rate, level, text = tooltip)) +
  geom_col(aes(x = 1, text = NULL), fill = "grey90", width = 0.8) +
  geom_col(fill = "steelblue", width = 0.8) +
  scale_x_continuous(expand = expansion(mult = c(0.01, NA)), labels = label_percent()) +
  labs(
    title = "Run rate by level",
    x = NULL,
    y = NULL
  ) +
  theme(
    panel.grid = element_blank(),
    axis.text.y = element_text(size = 11)
    )
  
ggplotly(p, tooltip = "text") |> 
  config(displayModeBar = FALSE) |> 
  layout(
    font = list(family = "Inter"),
    margin = list(t = 40, r = 20, b = 20, l = 20),
    xaxis = list(fixedrange = TRUE),
    yaxis = list(fixedrange = TRUE),
    hoverlabel = list(font = list(family = "Inter"))
    )
```

#### Sessions available by level

```{r}
p <- session_summary_level |> 
  mutate(
    tooltip = paste0(
      "<b>", level, "</b><br>",
      "Sessions available: ", n_session_avail, "<br>"
      )
    ) |> 
  ggplot(aes(n_session_avail, level, text = tooltip)) +
  geom_col(aes(x = 1, text = NULL), fill = "grey90", width = 0.8) +
  geom_col(fill = "steelblue", width = 0.8) +
  scale_x_continuous(expand = expansion(mult = c(0.01, NA))) +
  labs(
    title = "Number of sessions available by level",
    x = NULL,
    y = NULL
  ) +
  theme(
    axis.text.y = element_text(size = 11),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank()
    )

ggplotly(p, tooltip = "text") |> 
  config(displayModeBar = FALSE) |> 
  layout(
    font = list(family = "Inter"),
    margin = list(t = 40, r = 20, b = 20, l = 20),
    xaxis = list(fixedrange = TRUE),
    yaxis = list(fixedrange = TRUE),
    hoverlabel = list(font = list(family = "Inter"))
    )
```


### Fill rate {.tabset}

#### Fill rate total

```{r}
plot_ly(
  domain = list(x = c(0, 1), y = c(0, 1)),
  value = session_summary$fill_rate,
  title = list(text = "Fill rate"),
  type = "indicator",
  mode = "gauge+number",
  number = list(valueformat = ".0%"),
  gauge = list(
    bar = list(thickness = 1, color = "steelblue"),
    borderwidth = 0,
    steps = list(list(range = list(0, 1), color = "#e5e5e5")),
    axis = list(range = list(0, 1), tickformat = ".0%")
    )
  ) |> 
  config(displayModeBar = FALSE) |> 
  layout(
    font = list(family = "Inter"),
    margin = list(t = 40, r = 40, b = 10, l = 30)
    )
```

#### By level

```{r}
p <- session_summary_level |> 
  mutate(
    tooltip = paste0(
      "<b>", level, "</b><br>",
      "Fill rate: ", percent(fill_rate, 1), "<br>",
      "Spots filled: ", n_spots_filled, "<br>",
      "Spots available: ", n_spots_avail, "<br>"
      )
    ) |>   
  ggplot(aes(fill_rate, level, text = tooltip)) +
  geom_col(aes(x = 1, text = NULL), fill = "grey90", width = 0.8) +
  geom_col(fill = "steelblue", width = 0.8) +
  scale_x_continuous(
    expand = expansion(mult = c(0.01, NA)),
    labels = label_percent()
    ) +
  labs(
    title = "Fill rate by level",
    x = NULL,
    y = NULL
  ) +
  theme(
    axis.text.y = element_text(size = 11),
    panel.grid = element_blank()
    )
  
ggplotly(p, tooltip = "text") |> 
  config(displayModeBar = FALSE) |> 
  layout(
    font = list(family = "Inter"),
    margin = list(t = 40, r = 20, b = 20, l = 20),
    xaxis = list(fixedrange = TRUE),
    yaxis = list(fixedrange = TRUE),
    hoverlabel = list(font = list(family = "Inter"))
    )
```


#### Spots available by level

```{r}
p <- session_summary_level |> 
  mutate(
    tooltip = paste0(
      "<b>", level, "</b><br>",
      "Spots available: ", n_spots_avail, "<br>"
      )
    ) |> 
  ggplot(aes(n_spots_avail, level, text = tooltip)) +
  geom_col(aes(x = 1, text = NULL), fill = "grey90", width = 0.8) +
  geom_col(fill = "steelblue", width = 0.8) +
  scale_x_continuous(expand = expansion(mult = c(0.01, NA))) +
  labs(
    title = "Number of spots available by level",
    x = NULL,
    y = NULL
  ) +
  theme(
    axis.text.y = element_text(size = 11),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank()
    )

ggplotly(p, tooltip = "text") |> 
  config(displayModeBar = FALSE) |> 
  layout(
    font = list(family = "Inter"),
    margin = list(t = 40, r = 20, b = 20, l = 20),
    xaxis = list(fixedrange = TRUE),
    yaxis = list(fixedrange = TRUE),
    hoverlabel = list(font = list(family = "Inter"))
    )
```


# Court Usage Trends

## Column 1 {width=50%}

```{r}
p <- session_summary_trend |> 
  mutate(
    tooltip = paste0(
      "<b>", ym, "</b><br>",
      "Run rate: ", percent(run_rate, 1), "<br>",
      "Sessions run: ", n_session_run, "<br>",
      "Sessions available: ", n_session_avail, "<br>"
      )
  ) |> 
  select(ym, `Sessions available` = n_session_avail, tooltip, `Sessions run` = n_session_run, run_rate) |> 
  pivot_longer(-c(ym, run_rate, tooltip)) |> 
  ggplot(aes(ym, value, fill = name, text = tooltip)) +
  geom_col(position = position_dodge()) +
  scale_y_continuous(expand = expansion(mult = c(0.01, NA))) +
  scale_fill_manual(values = c("steelblue", "coral")) +
  labs(
    title = "Sessions available and run by month",
    x = NULL,
    y = NULL,
    fill = NULL
  ) +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text = element_text(size = 11)
    )
  
ggplotly(p, tooltip = "text") |> 
  config(displayModeBar = FALSE) |> 
  layout(
    font = list(family = "Inter"),
    margin = list(t = 40, r = 20, b = 20, l = 20),
    xaxis = list(fixedrange = TRUE),
    yaxis = list(fixedrange = TRUE),
    hoverlabel = list(font = list(family = "Inter")),
    legend = list(orientation = "h", xanchor = "right", yanchor = "bottom", x = 1, y = 1.02)
    
    )
```


```{r}
p <- session_summary_trend |> 
  mutate(
    tooltip = paste0(
      "<b>", ym, "</b><br>",
      "Fill rate: ", percent(fill_rate, 1), "<br>",
      "Spots filled: ", comma(n_spots_avail), "<br>",
      "Spots available: ", comma(n_spots_filled), "<br>"
      )
  ) |> 
  select(ym, `Spots available` = n_spots_avail, tooltip, `Spots filled` = n_spots_filled, fill_rate) |> 
  pivot_longer(-c(ym, fill_rate, tooltip)) |> 
  ggplot(aes(ym, value, fill = name, text = tooltip)) +
  geom_col(position = position_dodge()) +
  scale_y_continuous(labels = label_comma(), expand = expansion(mult = c(0.01, NA))) +
  scale_fill_manual(values = c("steelblue", "coral")) +
  labs(
    title = "Spots available and filled by month",
    x = NULL,
    y = NULL,
    fill = NULL
  ) +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text = element_text(size = 11)
    )
  
ggplotly(p, tooltip = "text") |> 
  config(displayModeBar = FALSE) |> 
  layout(
    font = list(family = "Inter"),
    margin = list(t = 40, r = 20, b = 20, l = 20),
    xaxis = list(fixedrange = TRUE),
    yaxis = list(fixedrange = TRUE),
    hoverlabel = list(font = list(family = "Inter")),
    legend = list(orientation = "h", xanchor = "right", yanchor = "bottom", x = 1, y = 1.02)
    
    )
```

## Column 2 {width=50%}

```{r}
p <- session_summary_level_trend |> 
  mutate(
    tooltip = paste0(
      "<b>", level, " — ", ym, "</b><br>",
      "Run rate: ", percent(run_rate, 1), "<br>",
      "Sessions run: ", n_session_run, "<br>",
      "Sessions available: ", n_session_avail, "<br>"
      )
  ) |> 
  ggplot(aes(ym, run_rate, color = level, text = tooltip, group = level)) +
  geom_line(lwd = 1) +
  geom_point(size = 2.5) +
  scale_color_manual(values = level_colors) +
  scale_y_continuous(labels = label_percent(), limits = c(0, 1)) +
  labs(
    title = "Run rate by level",
    x = NULL,
    y = NULL,
    color = NULL
  ) +
  theme(
    axis.text = element_text(size = 11)
    )

ggplotly(p, tooltip = "text") |> 
  config(displayModeBar = FALSE) |> 
  layout(
    font = list(family = "Inter"),
    margin = list(t = 40, r = 20, b = 20, l = 20),
    xaxis = list(fixedrange = TRUE),
    yaxis = list(fixedrange = TRUE),
    hoverlabel = list(font = list(family = "Inter")),
    legend = list(orientation = "h", xanchor = "right", yanchor = "bottom", x = 1, y = 1.02)
    )
```


```{r}
p <- session_summary_level_trend |> 
  mutate(
    tooltip = paste0(
      "<b>", level, " — ", ym, "</b><br>",
      "Fill rate: ", percent(fill_rate, 1), "<br>",
      "Spots filled: ", n_spots_avail, "<br>",
      "Spots available: ", n_spots_filled, "<br>"
      )
  ) |> 
  ggplot(aes(ym, fill_rate, color = level, text = tooltip, group = level)) +
  geom_line(lwd = 1) +
  geom_point(size = 2.5) +
  scale_color_manual(values = level_colors) +
  scale_y_continuous(labels = label_percent(), limits = c(0, 1)) +
  labs(
    title = "Fill rate by level",
    x = NULL,
    y = NULL,
    color = NULL
  ) +
  theme(
    axis.text = element_text(size = 11)
    )

ggplotly(p, tooltip = "text") |> 
  config(displayModeBar = FALSE) |> 
  layout(
    font = list(family = "Inter"),
    margin = list(t = 40, r = 20, b = 20, l = 20),
    xaxis = list(fixedrange = TRUE),
    yaxis = list(fixedrange = TRUE),
    hoverlabel = list(font = list(family = "Inter")),
    legend = list(orientation = "h", xanchor = "right", yanchor = "bottom", x = 1, y = 1.02)
    )
```

<!-- ```{r} -->
<!-- p <- by_player |>  -->
<!--   ggplot(aes(n)) + -->
<!--   geom_histogram(binwidth = 1, color = "white", fill = "steelblue") + -->
<!--   scale_x_continuous(expand = expansion(mult = c(0.01, NA))) + -->
<!--   scale_y_continuous(expand = expansion(mult = c(0.01, NA))) + -->
<!--   labs( -->
<!--     title = "How many sessions did each player attend in the month?", -->
<!--     x = "Number of sessions", -->
<!--     y = "Number of players" -->
<!--   ) + -->
<!--   theme_minimal() + -->
<!--   theme( -->
<!--     panel.grid.major.x  = element_blank(), -->
<!--     panel.grid.minor.x = element_blank(), -->
<!--     panel.grid.minor.y = element_blank() -->
<!--     ) -->

<!-- ggplotly(p) |>  -->
<!--   config(displayModeBar = FALSE) |>  -->
<!--   layout(font = list(family = "Inter")) -->
<!-- ``` -->


<!-- ```{r} -->
<!-- vbs <- list( -->
<!--   value_box( -->
<!--     title = "Unique players", -->
<!--     value = player_summary$n_players, -->
<!--     showcase = bs_icon("people"), -->
<!--     theme = value_box_theme(bg = "#FBF5E1", fg = "#A37E16") -->
<!--   ), -->
<!--   value_box( -->
<!--     title = "Mean sessions", -->
<!--     value = number(player_summary$mean, accuracy = 0.1), -->
<!--     showcase = bs_icon("bar-chart"), -->
<!--     theme = value_box_theme(bg = "#FBF5E1", fg = "#A37E16") -->
<!--   ), -->
<!--   value_box( -->
<!--     title = "Median sessions", -->
<!--     value = player_summary$median, -->
<!--     showcase = bs_icon("activity"), -->
<!--     theme = value_box_theme(bg = "#FBF5E1", fg = "#A37E16") -->
<!--   ), -->
<!--   value_box( -->
<!--     title = "Max sessions", -->
<!--     value = player_summary$max, -->
<!--     showcase = bs_icon("trophy"), -->
<!--     theme = value_box_theme(bg = "#FBF5E1", fg = "#A37E16") -->
<!--   )   -->
<!-- ) -->

<!-- layout_column_wrap(!!!vbs, width = 1/2) -->
<!-- ``` -->

# By Player

## Column 1 - value boxes {width=33%}

```{r}
#| content: valuebox
#| title: "Unique players"
list(
  icon = "people",
  color = "#D6EFE1",
  value = comma(player_summary$n_players)
)
```

```{r}
#| content: valuebox
#| title: "Mean sessions"
list(
  icon = "bar-chart",
  color = "#e6f2fd",
  value = number(player_summary$mean, accuracy = 0.1)
)
```

```{r}
#| content: valuebox
#| title: "Median sessions"
list(
  icon = "activity",
  color = "#FBF5E1",
  value = comma(player_summary$median)
)
```

```{r}
#| content: valuebox
#| title: "Max sessions"
list(
  icon = "trophy",
  color = "#F6CEFC",
  value = comma(player_summary$max)
)
```

## Column 2 - plots

```{r}
p <- by_player |> 
  ggplot(aes(total)) +
  geom_histogram(binwidth = 1, color = "white", fill = "steelblue") +
  scale_x_continuous(expand = expansion(mult = c(0.01, NA))) +
  scale_y_continuous(expand = expansion(mult = c(0.01, NA))) +
  labs(
    title = "How many sessions did each player attend in the month?",
    x = "Number of sessions",
    y = "Number of players"
  ) +
  theme(
    panel.grid.major.x  = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank()
    )

ggplotly(p) |> 
  config(displayModeBar = FALSE) |> 
  layout(font = list(family = "Inter"))
```

### Player DUPR range {.tabset}

#### Players by DUPR range
 
```{r}
p <- rating_player_summary |> 
  mutate(
    tooltip = paste0(
      "<b>", dupr_range, "</b><br>",
      "Number of players: ", n
      )
    ) |>
  ggplot(aes(n, dupr_range, text = tooltip)) +
  geom_col(fill = "steelblue", width = 0.8) +
  scale_x_continuous(expand = expansion(mult = c(0.01, 0.1))) +
  labs(
    title = "Number of players by DUPR range",
    x = NULL,
    y = NULL
  ) +
  theme(
    axis.text.y = element_text(size = 11),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank()
    )
  
ggplotly(p, tooltip = "text") |> 
  config(displayModeBar = FALSE) |> 
  layout(
    font = list(family = "Inter"),
    margin = list(t = 40, r = 20, b = 20, l = 20),
    xaxis = list(fixedrange = TRUE),
    yaxis = list(fixedrange = TRUE),
    hoverlabel = list(font = list(family = "Inter"))
    )
```

#### Avg sessions by DUPR range

```{r}
p <- player_summary_by_dupr_range |> 
  mutate(
    tooltip = paste0(
      "<b>", dupr_range, "</b><br>",
      "Average number of sessions played: ", number(mean, 0.1), "</b></br>",
      "Number of players: ", n_players
      )
    ) |>
  ggplot(aes(mean, dupr_range, text = tooltip)) +
  geom_col(fill = "steelblue", width = 0.8) +
  scale_x_continuous(expand = expansion(mult = c(0.01, 0.1))) +
  labs(
    title = "Average number of sessions played by DUPR range",
    x = NULL,
    y = NULL
  ) +
  theme(
    axis.text.y = element_text(size = 11),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank()
    )
  
ggplotly(p, tooltip = "text") |> 
  config(displayModeBar = FALSE) |> 
  layout(
    font = list(family = "Inter"),
    margin = list(t = 40, r = 20, b = 20, l = 20),
    xaxis = list(fixedrange = TRUE),
    yaxis = list(fixedrange = TRUE),
    hoverlabel = list(font = list(family = "Inter"))
    )
```

#### Avg DUPR by level

```{r}
p <- session_summary_level |> 
  mutate(
    tooltip = paste0(
      "<b>", level, "</b><br>",
      "Mean DUPR: ", number(mean_dupr, 0.01)
      )
    ) |>   
  ggplot(aes(mean_dupr, level, text = tooltip)) +
  geom_col(aes(x = 1, text = NULL), fill = "grey90", width = 0.8) +
  geom_col(fill = "steelblue", width = 0.8) +
  scale_x_continuous(
    expand = expansion(mult = c(0.01, NA)),
    labels = label_number(accuracy = 0.1)
    ) +
  labs(
    title = "Average DUPR rating by session level",
    x = NULL,
    y = NULL
  ) +
  theme(
    axis.text.y = element_text(size = 11),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank()
    )

ggplotly(p, tooltip = "text") |> 
  config(displayModeBar = FALSE) |> 
  layout(
    font = list(family = "Inter"),
    margin = list(t = 40, r = 20, b = 20, l = 20),
    xaxis = list(fixedrange = TRUE),
    yaxis = list(fixedrange = TRUE),
    hoverlabel = list(font = list(family = "Inter"))
    )
```


# Data Tables

## Tables {.tabset}

### Session detail

```{r}
to_table <- by_session |> 
  arrange(date_time, level) |> 
  transmute(
    session_id,
    level,
    date = force_tz(date_time, tzone = "America/New_York"),
    time = force_tz(date_time, tzone = "America/New_York"),
    weekday,
    weekday_sort = wday(date),
    day_part,
    day_part_sort = as.numeric(day_part),
    mean_dupr,
    registered,
    spots,
    fill_rate = pct_registered,
  )
  
to_table |> 
  reactable(
    filterable = TRUE,
    pagination = FALSE,
    highlight = TRUE,
    defaultSorted = "date",
    columns = list(
      date = colDef(format = colFormat(date = TRUE)),
      time = colDef(format = colFormat(time = TRUE)),
      weekday = colDef(show = FALSE),
      weekday_sort = colDef(
        name = "weekday",
        cell = function(value, i) {to_table$weekday[i]}
        ),
      day_part = colDef(show = FALSE),
      day_part_sort = colDef(
        name = "day part",
        cell = function(value, i) {to_table$day_part[i]}
        ),
      mean_dupr = colDef(name = "avg dupr", format = colFormat(digits = 1)),
      fill_rate = colDef(
        name = "fill rate",
        format = colFormat(digits = 0, percent = TRUE)
        # style = color_scales(to_table, opacity = 0.5)
        )
      )
    )
```

### Player detail


```{r}
by_player_play_up_down <- by_player |>
  pivot_longer(-c(player_id, player_name, dupr_id, rating),
               names_to = "level", values_to = "n") |> 
  filter(!level %in% c("total", "reliability"), n > 0) |> 
  arrange(player_id) |> 
  mutate(
    lower_lim = as.numeric(str_sub(level, 1, 3)),
    upper_lim = as.numeric(str_sub(level, 5, 7)),
    upper_lim = if_else(is.na(upper_lim), Inf, upper_lim),
    played_up = rating < lower_lim,
    played_down = rating > upper_lim,
    played_at_level = between(rating, lower_lim, upper_lim)
    ) |>
  select(player_id, rating, n, played_up, played_down, played_at_level) |> 
  pivot_longer(-c(player_id, rating, n)) |> 
  filter(value) |>
  group_by(player_id, name) |>
  summarize(n = sum(n)) |> 
  group_by(player_id) |> 
  mutate(pct = n / sum(n)) |> 
  ungroup() |> 
  select(-n) |> 
  pivot_wider(names_from = name, values_from = pct, values_fill = 0)
```


```{r}
by_player |> 
  left_join(by_player_play_up_down, join_by(player_id)) |> 
  arrange(desc(total)) |> 
  select(player_name, total, rating, reliability, `2.3–3.0`, `2.8–3.5`, `3.3–4.0`, `3.8–4.5`, `4.3+`, played_at_level, played_up, played_down) |> 
  reactable(
    filterable = TRUE,
    pagination = FALSE,
    highlight = TRUE,
    columns = list(
      player_name = colDef(name = "name"),
      total = colDef(name = "total sessions"),
      rating = colDef(
        name = "dupr rating",
        format = colFormat(digits = 1)
        ),
      reliability = colDef(name = "dupr reliability"),
      played_at_level = colDef(name = "% At level", format = colFormat(digits = 0, percent = TRUE)),
      played_up = colDef(name = "% Up", format = colFormat(digits = 0, percent = TRUE)),
      played_down = colDef(name = "% Down", format = colFormat(digits = 0, percent = TRUE))

      )
    )
```

<!-- ### Player detail -->

<!-- ```{r} -->
<!-- to_table <- session_player_long |>  -->
<!--   filter(!is.na(player_id)) |>  -->
<!--   arrange(player_id, date_time) |>  -->
<!--   transmute( -->
<!--     player_name, -->
<!--     level, -->
<!--     date = force_tz(date_time, tzone = "America/New_York"), -->
<!--     time = force_tz(date_time, tzone = "America/New_York"), -->
<!--     weekday, -->
<!--     weekday_sort = wday(date), -->
<!--     session_id -->
<!--   ) -->

<!-- to_table |>  -->
<!--   reactable( -->
<!--     filterable = TRUE, -->
<!--     pagination = FALSE, -->
<!--     highlight = TRUE, -->
<!--     columns = list( -->
<!--       date = colDef(format = colFormat(date = TRUE)), -->
<!--       time = colDef(format = colFormat(time = TRUE)), -->
<!--       weekday = colDef(show = FALSE), -->
<!--       weekday_sort = colDef( -->
<!--         name = "weekday", -->
<!--         cell = function(value, i) {to_table$weekday[i]} -->
<!--         )       -->
<!--       ) -->
<!--     ) -->
<!-- ``` -->

